### 2024-11-18 project2/nnMetamodels.tex
new figs

% Fill this table with new results
\begin{table}[ht!]
    \centering
    \footnotesize
    \begin{tabular}{lcccc}
    \toprule
    \textbf{Metamodel} & \textbf{\makecell{Capacity}} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
    \midrule
    MLR & $\num{241}$ & $0.706 (\pm 8.34\times 10^{-4})$ & $0.713 (\pm 2.67 \times 10^{-2})$ & $0.706 (\pm 3.44 \times 10^{-4})$ \\
    QPR & $\num{481}$ & $0.543 (\pm 8.27\times 10^{-4})$ & $0.554 (\pm 2.32 \times 10^{-2})$ & $0.544 (\pm 4.12\times 10^{-4})$ \\
    FNN & $\num{35009}$ & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
    RNN & $\num{32021}$ & $0.132 (\pm 0.008)$ & $0.137 (\pm 0.008)$ & $0.119 (\pm 0.008)$ \\
    LSTM & $\num{35729}$ & $0.075 (\pm 0.004)$ & $0.079 (\pm 0.005)$ & $0.063 (\pm 0.004)$ \\
    RNN$^*$\footnotemark & $\num{32021}$ & $0.109 (\pm 0.005)$ & $0.128 (\pm 0.005)$ & $0.109 (\pm 0.005)$ \\
    \bottomrule
    \end{tabular}
    \caption{Architectures and MSEs of metamodels for GMWB inner simulation model.}
    \label{tab:gmwb_arch}
\end{table}

@@

\textcolor{red}{Need to collect the result for RNN and LSTM}

@@

In our proposed two-stage procedure, the metamodel is used to identify the predicted tail scenario set, on which the standard nested simulation procedure is run in stage 2 to estimate the $95\%$-CVaR.
An accurate identification of the true tail scenarios is crucial.
In a two-stage procedure, metamodels' overall prediction errors measured by the MSEs in Table~\ref{tab:gmwb_arch} are not the determining factor, but their ability to effectively rank the scenarios by their \textbf{true} losses is most critical in producing accurate CVaR estimates. 
A metamodel that uses less safety margin to rank can save simulation budget in stage 2.

@@

\textcolor{red}{Need to separate the bad RNN from the good RNN for Figure~\ref{fig2:tailMatches}.}

@@

\textcolor{red}{Need to separate the bad RNN from the good RNN for Figure~\ref{fig2:CVaR95}.}
Lastly, we return to our original goal of estimating the $95\%$-CVaR of the dynamic hedging error.
Figure~\ref{fig2:CVaR95} shows the $95\%$-CVaR estimates for all five metamodels with different safety margins, averaged over $100$ macro replications.
Figure~\ref{subfig2:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig2:AllSafetyMargin}.
Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal (solid and dotted, respectively) lines in Figure~\ref{fig2:CVaR95}.
We observe that, with reasonable safety margins, the two-stage procedures with a LSTM metamodel consistently produce estimates that are as accurate as the standard procedure's estimate.
The amount of computational savings is substantial.
The LSTM is particularly superior to other metamodels as it accurately identifies the true tail scenarios and produces highly accurate CVaR estimates with small safety margins.
By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the LSTM metamodel is able to achieve a similar accuracy as the standard procedure with a much smaller simulation budget.
As the percentage of correctly identified tails approaches $100\%$, the two-stage procedure's CVaR estimates does not converge to the true CVaR but to the standard procedure's estimate.
This is because the two-stage procedure's CVaR estimates are based on the standard procedure's estimates on the predicted tail scenarios, and the standard procedure's estimates themselves are also noisy.

@@

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
        \textbf{Model}      & \textbf{Noise level}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
        \midrule
        LSTM                & $N=100$                & $0.075 (\pm0.004)$        & $0.079(\pm0.005)$     & $0.063 (\pm0.004)$ \\ 
        High-capacity LSTM  & $N=100$                & $0.068 (\pm0.004)$        & $0.102(\pm0.006)$     & $0.060 (\pm0.004)$ \\
        Difference          & $N=100$                & $-0.007$                  & $0.023$               & $-0.003$ \\
        \hline
        LSTM                & $N=10$                 & $0.195 (\pm0.001)$        & $0.193(\pm0.001)$     & $0.070 (\pm0.001)$ \\
        High-capacity LSTM  & $N=10$                 & $0.157 (\pm0.002)$        & $0.199(\pm0.002)$     & $0.065 (\pm0.001)$ \\
        Difference          & $N=10$                 & $-0.038$                  & $0.006$               & $-0.005$ \\
        \hline
        LSTM                & $N=1$                  & $1.366 (\pm0.006)$        & $0.781(\pm0.005)$     & $0.129 (\pm0.002)$ \\
        High-capacity LSTM  & $N=1$                  & $1.354 (\pm0.006)$        & $0.795(\pm0.005)$     & $0.149 (\pm0.002)$ \\
        Difference          & $N=1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
        \bottomrule
    \end{tabular}
    \caption{MSEs of LSTM metamodels.}
    \label{tab:lstm_arch}
\end{table}

The first two rows of Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their $95\%$ confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
The test errors are included as a practical measure of the metamodels' generalization ability to unseen noisy samples.
For this particular experiment, we are more interested in the true errors, which measure the metamodels' ability to learn the true feature-label relationship from the low-noise, medium-noise, and high-noise datasets.
We first observe that all the true errors are lower than the training errors, indicating that the LSTM metamodels generalize well to predicting the true losses.
Both LSTM metamodels are able to learn the true feature-label relationship from the low-noise and medium-noise datasets.
However, when the noise level is high, both LSTM metamodels have high true error.
The diffences in the errors between the LSTM metamodels are also reported in the last rows of Table~\ref{tab:lstm_arch}.
A positive difference indicates that the high-capacity LSTM has higher errors than the LSTM.
We observe that both LSTM metamodels have similar errors on the low-noise and medium-noise datasets.
However, when the noise level is high, the high-capacity LSTM has higher errors than the regular LSTM.
This is because the high-capacity LSTM has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
In contrast, the LSTM metamodel is more robust to label noise and is able to learn the true feature-label relationship better from the high-noise dataset.
In practice, since the true relationship is unknown, the true error is not readily available.
The test error approximates the true error and is directly observable.
The difference in test errors of the LSTM metamodels are inconsistent with the differences in true errors.
Therefore, test errors are not reliable indicators of the metamodels' noise tolerance.
For practical applications that utilize nerual networks as metamodels, we recommend not simulating the test scenarios.
Instead, we recommend simulating the true contract losses on a few tail and non-tail training scenarios to evaluate the metamodels' noise tolerance.

@@

\textcolor{red}{The $N=1$ plot is not valid}

>>>>

% Fill this table with new results
\begin{table}[ht!]
    \centering
    \footnotesize
    \begin{tabular}{lcccc}
    \toprule
    \textbf{Metamodel} & \textbf{\makecell{Capacity}} & \textbf{Training error} & \textbf{Test error} & \textbf{True error}\\
    \midrule
    MLR & $\num{241}$ & $0.706 (\pm 8.34\times 10^{-4})$ & $0.713 (\pm 2.67 \times 10^{-2})$ & $0.706 (\pm 3.44 \times 10^{-4})$ \\
    QPR & $\num{481}$ & $0.543 (\pm 8.27\times 10^{-4})$ & $0.554 (\pm 2.32 \times 10^{-2})$ & $0.544 (\pm 4.12\times 10^{-4})$ \\
    FNN & $\num{35009}$ & $0.129 (\pm 5.95\times 10^{-3})$ & $0.240 (\pm 9.82 \times 10^{-3})$ & $0.132 (\pm 5.82\times 10^{-3})$ \\
    RNN & $\num{32021}$ & $0.132 (\pm 7.53\times 10^{-3})$ & $0.137 (\pm 7.62\times 10^{-3})$ & $0.119 (\pm 7.51\times 10^{-3})$ \\
    LSTM & $\num{35729}$ & $0.075 (\pm 4.48\times 10^{-3})$  & $0.079 (\pm 5.35\times 10^{-3})$ & $0.063 (\pm 4.43\times 10^{-3})$ \\
    RNN$^*$\footnotemark & $\num{32021}$ & $0.109 (\pm 5.20\times 10^{-3})$  & $0.128 (\pm 5.22\times 10^{-3})$  & $0.109 (\pm 5.20\times 10^{-3})$ \\
    \bottomrule
    \end{tabular}
    \caption{Architectures and MSEs of metamodels for GMWB inner simulation model.}
    \label{tab:gmwb_arch}
\end{table}

@@

@@

In our proposed two-stage procedure, the metamodel is used to identify the predicted tail scenario set, on which the standard nested simulation procedure is run in stage 2 to estimate the $95\%$-CVaR.
An accurate identification of the true tail scenarios is crucial.
In a two-stage procedure, metamodels' overall prediction errors measured by the MSEs in Table~\ref{tab:gmwb_arch} are not the determining factor, but their ability to effectively rank the scenarios by their \textbf{true} losses is most critical in producing accurate CVaR estimates. 
A metamodel that uses less safety margin to rank can save more simulation budget in stage 2.

@@

@@

Lastly, we return to our original goal of estimating the $95\%$-CVaR of the dynamic hedging error.
Figure~\ref{fig2:CVaR95} shows the $95\%$-CVaR estimates for all five metamodels with different safety margins, averaged over $100$ macro replications.
Figure~\ref{subfig2:ZoomedSafetyMargin} is a zoomed version of Figure~\ref{subfig2:AllSafetyMargin}.
Because the safety margin only affects the two-stage procedure, the true 95\%-CVaR and the one estimated by the standard procedure are horizontal (solid and dotted, respectively) lines in Figure~\ref{fig2:CVaR95}.
We observe that, with reasonable safety margins, the two-stage procedures with a LSTM metamodel consistently produce estimates that are as accurate as the standard procedure's estimate.
The amount of computational savings is substantial.
The LSTM is particularly superior to other metamodels as it accurately identifies the true tail scenarios and produces highly accurate CVaR estimates with small safety margins.
By concentrating the simulation budget on the predicted tail scenarios, the two-stage procedure with the LSTM metamodel is able to achieve a similar accuracy as the standard procedure with a much smaller simulation budget.
As the percentage of correctly identified tails approaches $100\%$, the two-stage procedure's CVaR estimates does not converge to the true CVaR but to the standard procedure's estimate.
This is because the two-stage procedure's CVaR estimates are based on the standard procedure's estimates on the predicted tail scenarios, and the standard procedure's estimates themselves are also noisy.

@@

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
        \textbf{Model}      & \textbf{$N$}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
        \midrule
        LSTM                & $100$                & $0.075 (\pm4.5\times 10^{-3})$        & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
        High-capacity LSTM  & $100$                & $0.068 (\pm3.6\times 10^{-3})$        & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
        Difference          & $100$                & $-0.007$                  & $0.023$               & $-0.003$ \\
        \hline
        LSTM                & $10$                 & $0.195 (\pm1.1\times 10^{-3})$        & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
        High-capacity LSTM  & $10$                 & $0.157 (\pm2.0\times 10^{-3})$        & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
        Difference          & $10$                 & $-0.038$                  & $0.006$               & $-0.005$ \\
        \hline
        LSTM                & $1$                  & $1.366 (\pm8.6\times 10^{-3})$        & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
        High-capacity LSTM  & $1$                  & $1.354 (\pm2.7\times 10^{-2})$        & $0.795(\pm8.3\times10^{-2})$     & $0.149 (\pm2.7\times 10^{-2})$ \\
        Difference          & $1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
        \bottomrule
    \end{tabular}
    \caption{MSEs of LSTM metamodels.}
    \label{tab:lstm_arch}
\end{table}

The first two rows of Table~\ref{tab:lstm_arch} shows the average squared errors and the half widths of their $95\%$ confidence intervals between the metamodel predictions and the labels in the training dataset and the true dataset.
$N$ indicates the noise level in the training labels, i.e., a simulation dataset with fewer inner replications has a higher noise level.
The test errors are included as a practical measure of the metamodels' generalization ability to unseen noisy samples.
For this particular experiment, we are more interested in the true errors, which measure the metamodels' ability to learn the true feature-label relationship from the low-noise, medium-noise, and high-noise datasets.
We first observe that all the true errors are lower than the training errors, indicating that the LSTM metamodels generalize well to predicting the true losses.
Both LSTM metamodels are able to learn the true feature-label relationship from the low-noise and medium-noise datasets.
However, when the noise level is high, both LSTM metamodels have high true error.
The diffences in the errors between the LSTM metamodels are also reported in the last rows of Table~\ref{tab:lstm_arch}.
A positive difference indicates that the high-capacity LSTM has higher errors than the LSTM.
We observe that both LSTM metamodels have similar errors on the low-noise and medium-noise datasets.
However, when the noise level is high, the high-capacity LSTM has higher errors than the regular LSTM.
This is because the high-capacity LSTM has more trainable parameters and is more prone to over-fitting to the noise in the training labels.
In contrast, the LSTM metamodel is more robust to label noise and is able to learn the true feature-label relationship better from the high-noise dataset.
In practice, since the true relationship is unknown, the true error is not readily available.
The test error approximates the true error and is directly observable.
The difference in test errors of the LSTM metamodels are inconsistent with the differences in true errors.
Therefore, test errors are not reliable indicators of the metamodels' noise tolerance.
For practical applications that utilize nerual networks as metamodels, we recommend not simulating the test scenarios.
Instead, we recommend simulating the true contract losses on a few tail and non-tail training scenarios to evaluate the metamodels' noise tolerance.

@@
